Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2024-09-13 article.tex
Added Cooks membrane geometry and mesh image
Added narrowTmember geometry image

\paragraph{Case 3: Narrow T-section component under tension}
This case, proposed by \citet{Demirdzic1997}, consists of a narrow engineering component with a T cross-section (Figure \ref{fig:narrowTmember}).
The case is 3-D, static, with linear elastic material behaviour.
Symmetry allows one quarter of the geometry to be simulated.
A constant negative pressure of 1 MPa is applied to the lower surface and the upper left surface is fully clamped.
The Young’s modulus is $E = 210$ GPa and Poisson’s ratio is $\nu = 0.3$.
A hole of radius $5$ mm is located at the expected stress concentration.
\hl{Comment on the meshes}
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.2\textwidth]{figures/narrowTmember.pdf} 
   \includegraphics[width=0.2\textwidth]{figures/placeholder.pdf} 
   \caption{Inflation of an idealised ventricle case geometry, mesh and loading conditions}
   \label{fig:narrowTmember}
\end{figure}

@@

\paragraph{Case 5: Cook's membrane}
Cook's membrane (Figure \ref{fig:cooks_membrane}) is a well-known bending-dominated benchmark case used in linear and non-linear analysis.
In current work, the finite strain elastoplastic version \citep{Simo1992} is considered. \hl{We could also consider the small-strain elastic version if needed}
The 2-D tapered panel (trapezoid) is fixed on one side and subjected to uniform shear traction on the opposite side.
The prescribed shear traction is $\tau = 0.3125$ MPa.
The vertices of the trapezoid (in mm) are (0, 0), (48, 44), (48, 60),  and (0, 44).
There are no body forces, and the problem is solved as statically as 2-D plane strain.
The problem is solved as static, using 30 equally-sized loading increments.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.4\textwidth]{figures/cooksMembrane-geometry.png} 
   \caption{Cook's membrane case geometry (dimensions in mm) and loading conditions (fixed left, traction $\tau$ applied to right)}
   \label{fig:cooks_membrane}
\end{figure}

>>>>

\paragraph{Case 3: Narrow T-section component under tension}
This case, proposed by \citet{Demirdzic1997}, consists of a narrow engineering component with a T cross-section (Figure \ref{fig:narrowTmember}).
The case is 3-D, static, with linear elastic material behaviour.
Symmetry allows one quarter of the geometry to be simulated.
A constant negative pressure of 1 MPa is applied to the lower surface and the upper left surface is fully clamped.
The Young’s modulus is $E = 210$ GPa and Poisson’s ratio is $\nu = 0.3$.
A hole of radius $5$ mm is located at the expected stress concentration.
\hl{Comment on the meshes}
%\begin{figure}[htbp]
%   \centering
%   \includegraphics[width=0.4\textwidth]{figures/narrowTmember-geometry.pdf} 
%   \caption{Inflation of an idealised ventricle case geometry, mesh and loading conditions}
%   \label{fig:narrowTmember}
%\end{figure}
\\
\hl{Philip, so far I have been doing pictures in xfig which is a bit outdated so I am switching to inkscape. I know you have this image of geometry from your article, so feel free to replace it. I made it purely to practice inkscaping.}
\begin{figure}[H]
	\centering
	\subfigure[Case geometry (considered quarter geometry)]
	{
		\label{fig:ventricle_geometry}
   		\includegraphics[height=0.45\textwidth]{figures/narrowTmember-geometry} 
   	}
   	\qquad
	\subfigure[Mesh with 1,620 cells]
	{
		\label{fig:ventricle_mesh}
   		\includegraphics[height=0.4\textwidth]{figures/placeholder.pdf}  
   	}
	\caption{Narrow T-section component under tension.}
	\label{fig:narrowTmember}
\end{figure}

@@

\paragraph{Case 5: Cook's membrane}
Cook's membrane (Figure \ref{fig:cooks_membrane}) is a well-known bending-dominated benchmark case used in linear and non-linear analysis.
In current work, the finite strain elastoplastic version \citep{Simo1992} is considered. \hl{We could also consider the small-strain elastic version if needed}
The 2-D tapered panel (trapezoid) is fixed on one side and subjected to uniform shear traction on the opposite side.
The prescribed shear traction is $\tau = 0.3125$ MPa.
The vertices of the trapezoid (in mm) are (0, 0), (48, 44), (48, 60),  and (0, 44).
There are no body forces, and the problem is solved as statically as 2-D plane strain.
The problem is solved as static, using 30 equally-sized loading increments.
%\begin{figure}[htbp]
%   \centering
%   \includegraphics[width=0.4\textwidth]{figures/cooksMembrane-geometry} 
%   \caption{Cook's membrane case geometry (dimensions in mm) and loading conditions (fixed left, traction $\tau$ applied to right)}
%   \label{fig:cooks_membrane}
%\end{figure}
\begin{figure}[H]
	\centering
	\subfigure[Case geometry and dimensions]
	{
		\label{fig:ventricle_geometry}
   		\includegraphics[height=0.4\textwidth]{figures/cooksMembrane-geometry} 
   	}
   	\qquad
	\subfigure[Hexahedral mesh with 144 cells]
	{
		\label{fig:ventricle_mesh}
   		\includegraphics[height=0.4\textwidth]{figures/cooksMembrane-mesh}  
   	}
	\caption{Cook's mem.}
   \label{fig:cooks_membrane}
\end{figure}
